The Incredible Mutating Test Files! Smart Mutation for Binary Fuzzing

### 2013-10-23 docs/paper/paper.tex
some more to paper, abstract

>>>>

\section{Abstract}

Finding exploitable bugs in binaries is a difficult and lucrative endeavour. Fuzzing, or the feeding of random input into processes to try and detect vulnerable conditions [CITE], is one technique used by researchers and analysts. Applications tested for vulnerability discovery are often black boxes because source code is unavailable. This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce [CITES]. Among these issues are efficient and thorough dynamic taint analysis [CITE], the path explosion problem [CITE], and what we call the path exploration problem [CITE?]. Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky. The path explosion problem arises from the nature of assembly languages. Jump instructions, which may make up as much as X\% of machine instructions in programs [CITE], each multiply the total number of existing paths in a binary by two. Considering the size of binaries, this quickly leads to an un-tenably large set of possible paths to explore via conventional techniques like symbolic execution. And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way. Such automated exploit generation is the subject of much research [CITES].

Our works aims to reduce the severity of the latter two problems while being wary of the first during implementation. Instead of trying to eke out slightly more reasonable performance by using symbolic execution less or more wisely [CITE], we focus instead of using machine learning techniques to mutation previous input test cases in efficient ways, so that more paths are explored "naturely" by the test suite, and vulnerable conditions are more likely to be found.

In the hope of developing as scalable and re-usable a product as possible, we assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary.
